**OptiFit: a fast method for fitting amplicon sequences to existing OTUs**

### 2020-12-10 paper/paper.Rmd
Add code availability statement

### The OptiFit Algorithm

### Analysis Workflow

>>>>

### Sequence Data Processing Steps

### Benchmarking

### Data and Code Availability

TODO: cite all these dependencies

We implemented the analysis workflow in Snakemake and relied on Python, R, and
GNU bash. Dependencies include mothur v1.45.0, vsearch v2.13.3, numpy, R
Markdown, the Tidyverse metapackage, and the conda environment manager. A
reproducible version of the workflow, manuscript, and conda environment is
available at **TODO: UPDATED REPO LINK**.
